\documentclass[11pt,a4paper,sans]{moderncv}
\include{imports}
% ModernCV themes
\moderncvstyle{banking}                       % Style: casual, classic, banking, oldstyle, fancy
\moderncvcolor{blue}                          % Color: blue, orange, green, red, purple, grey, black

% Personal data
\name{Ankit}{Kumar}
%\title{Curriculum Vitae}                       % Optional title
\address{Khoury College of Computer Sciences, Northeastern University, Boston} % Optional address
\phone[mobile]{+1~(857)~869~5430}                % Phone number
\email{ankitkumar.itbhu@gmail.com}                   % Email address
\homepage{ankitku.github.io}                      % Personal website
\social[linkedin]{ankitkumar1988}                      % LinkedIn profile
\social[github]{ankitku}                        % GitHub profile

\begin{document}

%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace{-1cm}
\section{Professional Summary}
Experienced Applied Scientist with a background in finance and tech
industries, having worked at Rivos, Amazon, Morgan Stanley and
Olacabs, eager to leverage my academic expertise and
industry experience to implement formal methods in practical
applications, driving innovation and enhancing software quality in
real-world projects.

\section{Computer Skills}
C, C++, Java, Rust, Lisp, ACL2, ACL2 Sedan, Coq, Haskell, Emacs, Git,
\LaTeX

\section{Professional Experience}
\cventry{Summer 2023}{Member of Technical Staff, Intern}{Rivos
  Inc.}{Portland, OR, USA}{}{}
\begin{itemize}
\item Formalized and proved security properties
  about the page walk algorithm used by a RISC-V based hypervisor (high level model).
\item Reduced ($\approx10$x) the time required to prove existing security theorems
  stated in Jaspergold (low level model) from days to hours, by
  transferring some of the identified helpful lemma from the high
  level model.
\item ACL2, ACL2 Sedan, Jaspergold
\end{itemize}
\cventry{Summer 2022}{Applied Scientist Intern}{Amazon}{Minneapolis,
  MN, USA}{}{}
\begin{itemize}
  \item Created a tool to identify possible critical data leaks from
    AWS resources.
  \item Demonstrated the use of taint-analysis tools for cloud
    level tracking of critical data across AWS resources.
  \item Patented this technique, and received an incline offer
    from Amazon. 
  \item Java, Grails, github, shell scripting
\end{itemize}

\cventry{2012-2014}{Software Development Engineer
  II}{Olacabs}{Bengaluru, KA, India}{}{}
\begin{itemize}
\item Wrote the first version of the Olacabs (Indian ride-hailing app
  service, like Uber) android consumer app, responsible for over 80\%
  of all cab bookings.
  \item Debugged the Olacabs driver app, reducing instances of phone
    crashes by more than 60\%.
  \item Worked on cashless payment and online wallet systems. 
\end{itemize}

\cventry{2010-2012}{Associate}{Morgan Stanley Advantage
  Services}{Mumbai, MH, India}{}{}
\begin{itemize}
\item Refactored a derivatives trading platform to be region aware.
\item Rolled out the platform to new markets (HK, SG) which increased
  the number of trades it handled by more than 2x.
\end{itemize}


\section{Education}
\cventry{2018--2025}{PhD in Computer Science}{Northeastern
  University}{Boston, MA, USA}{}{Applied theorem proving, counter-example
  generation and the theory of refinement to analyze the Gossipsub
  P2P protocol. Also worked on automated feedback
  for homework submissions, proof checking and decision procedures for
  solving string equations.}
\quad\cvitem{Thesis}{Refinement based reasoning of P2P
  protocols is feasible and useful}

\cventry{2015--2017}{M.Tech in Computer Science}{IIT Kanpur}{Kanpur,
  UP, India}{}{}
\cventry{2006-2010}{B.Tech in Electrical Engineering}{IIT (BHU)
  Varanasi}{Varanasi, UP, India}{}{}

\bibliographystyle{IEEE}
\nocite{*}
\bibliography{pubs.bib}

\section{Awards and Honors}
\cvitem{Fellowship}{Dissertation Completion Fellowship during Summer
  2024.}
\cvitem{Invited Talk - Syracuse University 2024}{Formal Model-Driven Analysis of Resilience of GossipSub to Attacks from Misbehaving Peers}
\cvitem{Award}{Best Student Paper Award for our paper
  ``Verification of GossipSub in ACL2s''  at ACL2 Workshop 2023.}
\cvitem{Invited Talk - IPFS Camp at Lisbon,
  2022}{\href{https://www.youtube.com/watch?v=T3QLhijHAwA}{Formal
    Analysis of GossipSub : Property Driven Dev for Security}}
\cvitem{Fellowship}{Student Travel Fellowship to attend PLMW at POPL 2019 conference.}
\cvitem{Award}{\href{https://www.youtube.com/watch?v=AFact1zmnEM}{First Prize} at Droidcon India - Bangalore 2013 \href{https://www.youtube.com/watch?v=3qtuORgVMrQ}{Hackathon}}
\end{document}
